### 2014-03-05 src/methodology.Rnw
pdate

\subsection{Probes}

>>>>

\subsection{Sampling Criterias}

We used several different sampling criterias. The simplest one consisted of using x\% selection as suggested by Wong et al.~\cite{wong1995reducing}. Next, we looked at choosing x\% per program elements such as blocks, lines, method, and classes. Then in the interests of comparison to statement deletion operator, we chose the number of lines per program elements as the sampling criteria. We next extended this criteria by sampling the mutants thus produced again by half, quarter etc. Next, we looked at the impact of simply selecting a single mutant per program element, and extended it by reducing that even further by half quarter etc. Finally, as with statement deletion, we approximated other statement selection operators discussed in the literature (Wong, Offutt96, Javalanche, Namin08) as the operator selection criteria.
